\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-11-25 tex/paper.tex
Restructured the sections

\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{url}
\usepackage{float}
\usepackage{sectsty}
\usepackage{pdfpages}
\usepackage[section]{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}

\usepackage{setspace}
\usepackage[toc,page]{appendix}
\usepackage{framed}
\usepackage{geometry}

@@

\begin{document}

@@

%\includepdf[pages={1}]{abstract.pdf}
\begin{abstract}
    TODO: Abstract

@@

\newpage\null\thispagestyle{empty}\newpage

@@

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution
Network to be able to scale to a large user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then directly available to the public.  For secret content this can be a problem and that is
what this thesis is about. This work examines ways of enforcing access control on content and groups
of content in the form of folders and snapshots. A system was developed to make the underlying
theory work in practice.

@@

\newpage 
\section{Model}
\subsection{Entities}
%\subsubsection*{snapshot} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{Content}
Content is meta data about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.

\subsubsection{Project}
A project is what is created to contain all content and containers related to a real project. Files
can be changed within a project and the system can contain several projects and their virtual
content are completely disjoint.

\subsubsection{Container}
A container is a virtual folder within a project which can contain content and other containers.

\subsubsection{Snapshot}
A snapshot is a read-only container from the state which the container the was in when the snapshot
was created.  A snapshot can not be updated and can only be deleted from the root of the snapshot.
Snapshots are by default stored as siblings to the container which they were made from, but they can
be contained by any container.

\subsubsection{File}
A file refers to an actual physical file. Files are stored in the database to make backup,
deployment and migration easier.

\subsubsection{User}
A user is the structure that handles people who have been granted access to the system.  Access to
the system is handled by a separate service, like LDAP.

\subsection{JPF}
Java path finder was used to show that the model and plan of how to build the system was sound. The
model was built in Java with the objective of being as reduced and simple as possible, without
loosing any of the cases that needed to be covered by the model checker. As the users are mainly
going to be handled by external systems they were not included in the model.

ConcurrentHashMap had to be used in favour of the normal HashMap as the normal HashMaps can't be
iterated over concurrently.

\newpage 
\section{Snapshots}
Write what snapshots are
\subsection{Copy-on-Write}
\label{sec:copy-on-write}
To efficiently create snapshots of a system Copy-on-Write can be used to make it possible to create
snapshots in O(1)\cite{BTRFS}, this is due to the fact that to create a snapshot in a system using
Copy-on-Write you only need to reference the current nodes in the tree and make sure that they are
not removed, see Figure~\ref{fig:btrfs_tree}.

@@

\subsection{Snapshots}
This implementation is far from as efficient as the other Copy-on-Write systems described in
Section~\ref{sec:copy-on-write} in most aspects, but more efficient in some. As the implementation
is built upon MongoDB as persistent storage and not a pure tree structure, single nodes can be
fetched in O(1) but when querying for subtrees they need to be built first, which takes O(log(n)),
where n is the number of nodes in the subtree.

In Perius snapshots and clones are not taken in the fashion which Btrfs uses, which can be seen in
Figure~\ref{fig:btrfs_tree}. As Perius does not have the tree structure pre-built and each node is
instead stored in a flat storage space, such operation would be too computationally expensive as
trees would have to be merged when collisions occur, due to the non-blocking nature of the
application. Instead this implementation makes a full copy of the meta-data of the tree, but still
refers to the same binary files until they are changed, which results in the creation of a new node.

@@

\subsection{Resulting system}
\subsubsection{Persistent storage}
\label{persistent_storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its
internal storage format called BSON, which is very similar to JSON which the API is using. As the
formats are similar, the process of marshalling and unmarshalling becomes quite easy between the
core code, MongoDB instance and REST interface.  The second reason was that if the system needs to
scale in the future it is very easy to distribute MongoDB and if needed the system can easily be
migrated to Reactive Mongo, which is an asynchronous and non-blocking driver for MongoDB and can
therefore make the system scale even further~\cite{REACTIVEMONGO}.

@@

@@

>>>>

%{{{
\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{url}
\usepackage{float}
\usepackage{sectsty}
\usepackage{pdfpages}
\usepackage[section]{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{setspace}
\usepackage[toc,page]{appendix}
\usepackage{framed}
\usepackage{geometry}

@@

%}}}

%{{{
\begin{document}

@@

%\includepdf[pages={1}]{abstract.pdf}

%}}}
\begin{abstract}
    TODO: Abstract

@@

%{{{
\newpage\null\thispagestyle{empty}\newpage

@@

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}

%}}}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution
Network to be able to scale to a large user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then directly available to the public.  For secret content this can be a problem and that is
what this thesis is about. This work examines ways of enforcing access control on content and groups
of content in the form of folders and snapshots. A system was developed to make the underlying
theory work in practice.

@@

\newpage 
\newpage 
\section{Snapshots}
Write what snapshots are
\subsection{Copy-on-Write}
\label{sec:copy-on-write}
To efficiently create snapshots of a system Copy-on-Write can be used to make it possible to create
snapshots in O(1)\cite{BTRFS}, this is due to the fact that to create a snapshot in a system using
Copy-on-Write you only need to reference the current nodes in the tree and make sure that they are
not removed, see Figure~\ref{fig:btrfs_tree}.

@@

\subsection{Model}
\subsubsection{Entities}
%\subsubsection*{snapshot} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsubsection{Content}
Content is meta data about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.

\subsubsubsection{Project}
A project is what is created to contain all content and containers related to a real project. Files
can be changed within a project and the system can contain several projects and their virtual
content are completely disjoint.

\subsubsubsection{Container}
A container is a virtual folder within a project which can contain content and other containers.

\subsubsubsection{Snapshot}
A snapshot is a read-only container from the state which the container the was in when the snapshot
was created.  A snapshot can not be updated and can only be deleted from the root of the snapshot.
Snapshots are by default stored as siblings to the container which they were made from, but they can
be contained by any container.

\subsubsubsection{File}
A file refers to an actual physical file. Files are stored in the database to make backup,
deployment and migration easier.

\subsubsubsection{User}
A user is the structure that handles people who have been granted access to the system.  Access to
the system is handled by a separate service, like LDAP.

\subsubsection{JPF}
Java path finder was used to show that the model and plan of how to build the system was sound. The
model was built in Java with the objective of being as reduced and simple as possible, without
loosing any of the cases that needed to be covered by the model checker. As the users are mainly
going to be handled by external systems they were not included in the model.

ConcurrentHashMap had to be used in instead of the normal HashMap, as the normal HashMaps can't be
iterated over concurrently.

\subsection{Snapshot functionality}
In Perius snapshots and clones are not taken in the fashion which Btrfs uses, which can be seen in
Figure~\ref{fig:btrfs_tree}. As Perius does not have the tree structure pre-built and each node is
instead stored in a flat storage space, such operation would be too computationally expensive as
trees would have to be merged when collisions occur, due to the non-blocking nature of the
application. Instead this implementation makes a full copy of the meta-data of the tree, but still
refers to the same binary files until they are changed, which results in the creation of a new node.

@@

\subsection{Resulting system}
This implementation is far from as efficient as the other Copy-on-Write systems described in
Section~\ref{sec:copy-on-write} in most aspects, but more efficient in some. As the implementation
is built upon MongoDB as persistent storage and not a pure tree structure, single nodes can be
fetched in O(1) but when querying for subtrees they need to be built first, which takes O(log(n)),
where n is the number of nodes in the subtree.

\subsubsection{Persistent storage}
\label{persistent_storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its
internal storage format called BSON, which is very similar to JSON which the API is using. As the
formats are similar, the process of marshalling and unmarshalling becomes quite easy between the
core code, MongoDB instance and REST interface.  The second reason was that if the system needs to
scale in the future it is very easy to distribute MongoDB and if needed the system can easily be
migrated to Reactive Mongo, which is an asynchronous and non-blocking driver for MongoDB and can
therefore make the system scale even further~\cite{REACTIVEMONGO}.

@@

%{{{

@@

%}}}
